\documentclass[12pt,letterpaper]{article}

\begin{document}

{\Large\center\textbf{Personal Statement} \\}

\vspace{2mm}

% Robotics interests and future career goals
Since my arrival at Oregon State University and the beginning of my formal
Computer Science education, I have been interested in applications of Computer
Science to the field of robotics. In particular, I am interested in computer
vision and its uses in robot navigation. These topics fascinate me because of
their wide-reaching applicability. There are so many fields that could benefit
from robots that are able to interpret and act upon their environments, from
manufacturing to agriculture to cinematography, that the number of exciting
challenges we have yet to overcome are virtually innumerable.

% Previous research or robotics experience
% - Aerial team
% - RDML
I began working with robotics my freshman year through the OSU Robotics Club. I
joined the Autonomous Aerial Robotics Team and immediately began working on the
team's autonomous navigation stack. This involved researching existing
navigation algorithms, communicating hardware needs with the rest of the team,
and implementing software to fit our requirements. Now, two years later, I have
taken over as team lead for the Aerial Team. I am responsible for overseeing all
team activities, coordination competitions, contacting sponsors, and working on
the robots themselves. I have worked directly on aerial vehicle flight control,
vision, and path planning systems. I have also had the opportunity to learn a
great deal about the mechanical and electrical aspects of robotics.

Through my involvement with the club I have also begun working at the OSU
Robotic Decision Making Laboratory. We are researching low-cost multi-robot
autonomous aerial vehicle exploration tasks. We have developed and simulated a
new algorithm for autonomous cooperative exploration with limited communication,
and are currently in the process of testing it on a custom aerial vehicle
platform.

% Anything else
Conducting research over the summer as part of the REU program will allow me to
continue to learn about and explore the field of robotics. I hope to learn more
about graduate school and gather experience to apply to a career in robotics.

\end{document}
